Generate Networks

### 2015-09-16 code/01_generate_networks.Rmd
scripts to calculate all possible maximum matchings in the networks
change data saving structure

```{r}
data <- read.csv("./data/bartomeus/Bartomeus_Ntw_nceas.txt",sep="\t") %>%
	tbl_df() %T>% print(width = Inf)

@@

saveRDS(networks, "./data/bartomeus/networks.dat", ascii = TRUE, compress = FALSE)
```

>>>>

```{r}
data <- read.csv("./data/Bartomeus_Ntw_nceas.txt",sep="\t") %>%
	tbl_df() %T>% print(width = Inf)

@@

for(i in 1:length(networks)){
	saveRDS(networks[[i]],
					paste0("./data/networks/", names(networks)[i], ".dat"),
					ascii = TRUE, compress = FALSE)
}

```
